\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

\title{Dr. Hellgie Talk Questionaire}

\author{Matthew W. Flickner}

\date{\today}

\begin{document}
\maketitle

\section{Give at least two specific examples of objects or behaviors that cognitive psychologists study?}
Cognitive psychologists study split brain patients with severed corpus callosums to better understand what each half of the brain does. They also study patients with local brain injuries such as damages to Broca's or Wernicke's areas which give them better understanding of where language and speech is located in the brain.

\section{How do these subjects of study relate to what interaction design studies?}
The subjects relate in the sense that both study the visual input on the brain and how the subject reacts to the input or what they expect following a certain visual cue, whether it be a visual psychological test or a computer software.

\section{Give at least two specific methods used by cognitive psychologists to study or learn about their subjects}
Cognitive psychologists use visual tests on split brain patients to see which side of their brain picks up which visual cues. They also use reading tests on patients with damage to Broca's and Wernicke's area to test how they can speak and respond to speech and syntax.

\section{How do these methods of study relate to how interaction design research is formed?}
Interaction design research is similar in that both cognitive psychologists and interaction design researchers do tests to see if users pick up visual cues and auditory cues. Interaction designers test for visual cues on computer screens and work with audio related cues when designing software that utilizes voice commands.




\end{document}